Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-11-19 proposalPres.tex
Update proposalPres.tex
I added a picture to the problem statement slide, and I still need to figure out how to position it. I also made edits to the Parts List and Concluding Remarks slides.

\begin{frame}{Problem Statement}
  \begin{block}{Problem Statement}
      Model different subsystems for an autonomous vehicle (Lexus platform is considered in this project), which are
      \begin{itemize}
          \item Steering
          \item Acceleration
          \item Brake
          \item Shift
          \item Speed
          \item Speed control
        \end{itemize} 
        using input-output raw data available offline
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{large}
      A potential solution is to develop conventional System Identification techniques for modeling subsystems using available raw data.  
    \end{large}
  \end{block}
\end{frame}

@@

\begin{frame}{Parts List}
  \begin{block}{Software and Hardware}
 \begin{itemize}
        \item Software
        \begin{itemize}
        \small
        \item MATLAB's System Identification Toolbox
        \item Vector CANAlyzer
        \end{itemize}
	\item Hardware
	\begin{itemize}
	\small
	\item Laptop
	\item PAC Mod
	\item CAN Case 
	\item CAN Bus
	\end{itemize}
\end{itemize}
  \end{block}
\end{frame}

@@

\section{Concluding Remarks}
\begin{frame}{Concluding Remarks}
  \begin{block}{Project goals}
    %\begin{LARGE}
      \begin{itemize}
        \item Develop models of an autonomous vehicle's subsystems, which are 
        \begin{itemize}
          \item Steering %  Model
          \item Acceleration % Model
          \item Brake % Model
          \item Shift % Model
          \item Speed % Model
          \item Speed control %Model
        \end{itemize}
      \end{itemize}
    %\end{LARGE}
  \end{block}
  \begin{block}{Anticipated Challenges}
    \begin{itemize}
      \item Achieving an acceptable accuracy and reliability for each model due to nonlinearities over small changes of command inputs, such as steering angle, $\ldots$
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}{Problem Statement}
  \begin{block}{Problem Statement}
      Model different subsystems for an autonomous vehicle (Lexus RX450H platform is considered in this project), which are
      \begin{itemize}
          \item Steering
          \item Acceleration
          \item Brake
          \item Shift
          \item Speed
          \item Speed control
        \end{itemize} 
        using input-output raw data available offline

          \begin{figure}
			\centering
			\begin{minipage}[t]{0.4\textwidth}
				%\centering
				\includegraphics[height=1.5cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
				\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}

			\end{minipage}
			\end{figure}
  \end{block}

  \pause
  \begin{block}{Proposed Solution}
    \begin{large}
      A potential solution is to develop conventional System Identification techniques for modeling subsystems using available raw data.  
    \end{large}
  \end{block}
\end{frame}

@@

\begin{frame}{Parts List}
  \begin{block}{Software and Hardware}
 \begin{itemize}
        \item Software
        \begin{itemize}
        \small
        \item MATLAB's System Identification Toolbox
        \item Vector CANAlyzer
        \end{itemize}
	\item Hardware
	\begin{itemize}
	\small
	\item Laptop
	\item PACMod ECU
	\item CANCase 
	\item CAN bus
	\end{itemize}
\end{itemize}
  \end{block}
\end{frame}

@@

\section{Concluding Remarks}
\begin{frame}{Concluding Remarks}
  \begin{block}{Project goals}
    %\begin{LARGE}
      \begin{itemize}
        \item Develop reliable and accurate models of an autonomous vehicle's subsystems 
        \item Help further the work on autonomous vehicle development
%        \begin{itemize}
%          \item Steering %  Model
%          \item Acceleration % Model
%          \item Brake % Model
%          \item Shift % Model
%          \item Speed % Model
%          \item Speed control %Model
%        \end{itemize}
      \end{itemize}
    %\end{LARGE}
  \end{block}
  \begin{block}{Anticipated Challenges}
    \begin{itemize}
      \item Achieving an acceptable accuracy and reliability for each model due to nonlinearities over small changes of command inputs, such as steering angle
    \end{itemize}
  \end{block}
\end{frame}
